### 2019-11-07 report/paper.tex
Add a bit of conclusion (can be improved)

\section{Conclusion}
In this project, we ...

>>>>

Maybe we can talk about the methods we also tried but didn't work/didn't use for the final solution here(?)

\section{Conclusion}
In this project, we managed to make use of several computer vision techniques and algorithms that we had learnt in class, and put them into practice. Although the results are not perfect, with the presence of several false positives, we managed to be able to detect some instances of the characters using our proposed solution. Which, given the timeline and schedule, is quite an achievement in its own.
